%! Author = nikitabarskov
%! Date = 4/9/22
% !TEX program = xelatex
% !TEX encoding = utf8

\documentclass[12pt]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

\setlength{\parindent}{0pt}

\usepackage{geometry}
\geometry{a4paper, left=10mm, right=10mm, bottom=10mm, top=10mm}
\pagestyle{empty}

\usepackage{tipa}
\usepackage{enumitem}

% Document
\begin{document}

\begin{center}
	\textbf{Barskov Nikita} \\
	\textipa{[baSkuv nIkit@]} \textbullet \ he \slash \ him \\
	\hrulefill
\end{center}

\begin{center}
	Oslo, Norway \textbullet \ nbarskov@gmail.com \textbullet \ +47 94 19 33 14 \textbullet \ linkedin.com/in/nikitabarskov \\
\end{center}

Software engineer with over 7 years of experience, specialising in data and machine learning.
Committed to building products using modern software practices and delivering value with
essential attention to detail.

\hrulefill

\begin{center}
	\textbf{Experience}
\end{center}

\textbf{Volur} \hfill Oslo, Norway \\
\textbf{Senior Software Enginer} \hfill May 2022 – \textit{Now}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
	\item Directing the data team's efforts as the engineering leader, designing data models and processing pipelines, creating internal and external APIs, and managing the underlying infrastructure.
	\item Improving processes and contributing to building a scalable product in the company by advocating modern software development practices like containerisation, continuous delivery, API First, infrastructure as code, platform engineering, and team topologies.
	\item Mentoring junior developers and advising on secure and reliable software development practices.
\end{itemize}

\vspace{10pt}

\textbf{Coop Norge} \hfill Oslo, Norway \\
\textbf{Senior Software Enginer} \hfill April 2021 – April 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
	\item Lead the Analytics Platform team to support analysts and data scientists in delivering insights and models.
	\item Played a key role in the development team responsible for delivering a new backend for the Coop Norge OBS! Bygg customer leaflet within the Coop mobile application.
	\item Enhanced processes and played a central role in implementing modern data warehouse architecture, Data Mesh, to build a scalable product within the company.
	\item Contributed to the development of the internal developer platform.
\end{itemize}

\vspace{10pt}

\textbf{Rystad Energy} \hfill Oslo, Norway \\
\textbf{Software Engineer} \hfill September 2019 – March 2021

\vspace{10pt}

\textbf{Inventale} \hfill Samara, Russian Federation \\
\textbf{Software Engineer} \hfill September 2017 – August 2019

\vspace{10pt}

\textbf{Cxense} \hfill Samara, Russian Federation \\
\textbf{Intern} \hfill September 2017 – August 2019

\hrulefill

\begin{center}
	\textbf{Education}
\end{center}

\textbf{Samara State Aerospace University} \hfill Samara, Russian Federation \\
Master of Informatics and Computer Engineering (with Honours) \hfill 2019

\textbf{Samara State Aerospace University} \hfill Samara, Russian Federation \\
Bachelor's Degree in Applied Physics and Mathematics \hfill 2017

\hrulefill

\begin{center}
	\textbf{Skills}
\end{center}

\textit{Technical}: Golang, Python, dbt, Golang, Python, dbt, gRPC, Protobuf, Open Container Initiative, Kubernetes, OpenTofu \slash Terraform, OpenTelemetry, GitHub Actions, Snowflake, Azure, Google Cloud. \\
\textit{Language}: English, Norwegian, Russian. \\
\textit{Soft skills}: pragmatic and rational, with a keen focus on teamwork and delivering value, excel in collaborative environments, problem-solver, quickly adopt to the changing environment and maintain positive attitude in the high pressure situations.

\end{document}
