\documentclass[12pt]{article}

\usepackage[left=0.5cm, right=0.5cm, top=0.5cm, bottom=0.5cm, bindingoffset=0cm]{geometry}

\usepackage[english,russian]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{multicol}
\usepackage{parskip}

\usepackage{fontspec}
\usepackage{fontawesome}

\pagenumbering{gobble}

\usepackage{ragged2e}
\usepackage{microtype}

\justifying
\sloppy
\tolerance=1000
\hyphenpenalty=10000
\emergencystretch=3em

\begin{document}
    \textbf{Barskov Nikita}
    \begin{multicols}{2}
        Data Engineer at Maxifier. \\
        Master Degree Student \\
        at Samara University.
        \begin{description}
            \item[\faMapPin] Samara, Russia
        \end{description}
        \columnbreak
        \begin{description}
            \item[\faPhone] \texttt{+7(927)657-16-10}
            \item[\faGithub] \texttt{github.com/nikitabarskov}
            \item[\faLinkedin] \texttt{linkedin.com/in/nikitabarskov}
            \item[\faPaperPlane] \texttt{t.me/nikitabarskov}
        \end{description}
    \end{multicols}
    \subsection*{Professional Summary}
    I am a data engineer, an enthusiast for developing intelligent and modern applications that improve the quality
    of using and presenting data. I've got 2 years experience with implementing ETL with frameworks such as
    Apache Spark, Apache Hadoop, Apache Mesos. I'm well known in Python data analysis libraries, mathematical packages,
    and visualization tools.

    I'm a bachelor of applied mathematics and physics with close to excellent average score (4.75/5.0). All mathematical
    and software engineer exercises have done with excellent score. My academic mathematical background allows me to
    take advantages of statistic, calculus and algebra methods for transforming data as I need and extracting necessary
    information for my work and needs.

    Now, I'm a student at Samara University with an excellent (5.0/5.0 at the moment) average score. Masters programme
    "Data Mining and Quality Assurance" contains courses about software lifecycle, testing, basic business analysis
    knowledge and fundamentals of machine learning. My Master's thesis theme is <<Forecasting users interacting with
    advertising content on sites>> and it absolutely relates with my current job specific.
    \subsection*{Experience}
    \subsubsection*{Maxifier, Samara, Russia}
    \textbf{Intern} \hfill April 2017 -- June 2017\\
    Working on batch processing project in Maxifier as Intern. \\
    Stack: Java, Guice, PostgreSQL, Spark, Hadoop, Aurora, Bazel, GitLab CI. \\
    \textbf{Data Engineer} \hfill June 2017 -- Present\\
    Developing the application for forecasting users interactions with advertising content and its evaluation. \\
    Stack: Python/Scala, Spark, Hadoop, Mesos, Docker, MySQL, Akka, Slick, SciPy, Maven, GitHub.
    \subsection*{Education}
    \subsubsection*{Samara University, Samara Russia}
    \textbf{Master Degree Student}\hfill \hfill September 2017 -- Present\\
    Data Analysis and Quality Assurance, Average Point 5.0\\
    \textbf{Bachelor of Science} \hfill Sep 2013 -- June 2017\\
    Applied Mathematics and Physics, Average Point 4.75
    \newpage
    \subsection*{Skills}
    \textbf{Personal:} rational, responsible, sociable \\
    \textbf{Base Skills:} advanced knowledge in mathematics and application of these methods to ETL \\
    \textbf{Natural Languages:} Russian (native), English (intermediate) \\
    \textbf{Programming Languages:} \texttt{Python 3} (intermediate knowledge for writing batch processing jobs and data
    science), \texttt{Scala, Java} (regular knowledge for writing services and batch processing jobs) \\
    \textbf{Frameworks and libraries:} Apache Spark, Apache Hadoop, Apache Mesos, Docker, Scipy(Pandas, Numpy,
    Matplotlib), Scikit-learn, Akka, Slick \\
    \textbf{Build Tools and VCS:} Maven, Bazel, Git, Gitlab CI, Github \\
    \textbf{Others:} fundamental knowledge about the development process (Process Cycle of Software Applications
    Development, methodologies, QA(methods and approaches), Bussiness and System Analytics(methods and approaches))
\end{document}
  